Depression and suicidality as costly signals of need

### 2021-04-08 Paper.rmd
Added line clarifying our use of the term signal in the methods section
Added citations for signals steming from cues.

As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than. The full text for the signals are available in the SI.

>>>>

As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than. Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [For discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015]. The full text for the signals are available in the SI.
